\LARGE \bf Optimal Joint Probabilistic Data Association Filter\\ Avoiding Coalescence in Close Proximity

### 2018-06-09 Conference/ECC 2014/ECC14_Lee.tex
added Conference folder

\documentclass[letterpaper, 10pt, conference]{ieeeconf}
\IEEEoverridecommandlockouts \overrideIEEEmargins
\usepackage{amsmath,amssymb,url}
\usepackage{graphicx,subfigure,tikz}
\usepackage{color}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}

@@

\title{\LARGE \bf
%Recursive Kalman-Mahanobis JPDAF Minimization to avoid Coalescence of Estimates in Close Proximity
Coalescence Avoiding Optimal Joint Probabilistic Data Association Filter}
\author{Evan Kaufman and Taeyoung Lee
 \thanks{Evan Kaufman and Taeyoung Lee are with Department of Aerospace Engineering, George Washington University, Washington, DC. Email: {\tt\footnotesize \{evankaufman, tylee\}@gwu.edu }}
}

\newcommand{\EditTL}[1]{{\color{red}\protect #1}}
\renewcommand{\EditTL}[1]{{\protect #1}}

@@

\begin{abstract}
This paper deals with an estimation problem where a known number of targets in close proximity are observed but the measurement originations are uncertain. It is well known that joint probabilistic data association filters (JPDAF) are effective in handing uncertain measurement originations with clutters, but they are prone to estimation coalescence, particularly when close neighboring targets share measurements. This paper proposes a Coalescence Avoiding Optimal JPDAF (C-JPDAF) that minimizes the weighted sum of the posterior uncertainty and a measure of similarity between estimated probability densities. The proposed approach has simpler structures than other coalescence avoiding approaches based on pruning, while exhibiting excellent filtering performance for targets in close proximity with crossing tracks. These are illustrated by a numerical example of two satellites on crossing orbits around the Earth.
%The algorithm is derived and explained, involving a higher computational cost that the JPDAF, but not high enough to prevent the possibility real-time implementation. A numerical example demonstrates how the C-JPDAF is able to maintain the correct trajectories of slowly crossing estimates whereas the JPDAF is not. The results show that the Kalman gain is an effective initial guess for the C-JPDAF, and we discuss the circumstances that warrant the algorithm's use.
\end{abstract}

@@

A variety of data association techniques are considered for the close-proximity data association with varying performance.
Some approaches such as multiple hypothesis tracking (MHT) and probability hypothesis density (PHD) techniques involve a high computational load, especially when targets are in close proximity, making real-time implementation more difficult~\cite{MHT1},~\cite{PHD1}, and~\cite{PHD2}.
Many other techniques may involve the Kalman filter (KF) or extended KF (EKF), which are well studied and provide a framework for recursive data association techniques that are much easier to implement in real-time.
A common heuristic approach is known as the nearest neighbor filter (NNF), which is a simple algorithm that only updates estimates for measurements with the closest square Mahalnobis distance, updating other targets only with their predictions~\cite{NN2}.
This is considered a \emph{hard decision} in~\cite{JPDAF1}, or that every measurement update receives full weighting; if the decision is incorrect, these measurement updates can result in detrimental effects to the associations of the estimates, so this technique is avoided in the analysis of this paper.
Alternatively, some approaches calculate the minimum mean square error (MMSE) of the estimates and their associated uncertainty.
The probabilistic data association (PDA) technique is effective in tracking a single target because it updates with a \emph{soft decision}; in particular, this approach updates provides a weighting from a likelihood of measurement association.

@@

% Dr. Lee Edits:
\section{Data Association Filtering Problem Formulation}
\label{ProbDef}

@@

More explicitly, let $\Theta_i$ be the event that the measurement originated from the $i$-th target, for $i\in\{1,2\}$. According to the above assumptions, we have
\begin{align}
P(\Theta_1\cup \Theta_2)&=1,\quad
P(\Theta_1\cap \Theta_2)=0,\\
P(\Theta_1)&=P(\Theta_2)=0.5.\label{eqn:MeaOrig}
\end{align}

@@

Joint probabilistic data association filter is a suboptimal Bayesian filter for multiple targets where the probabilities of association is computed for the latest set of measurements only~\cite{TrackDataAssoc}. This section summarizes the approaches of JPDAF.

@@

The data association probability is defined as follows. Let $\beta_i$ be the probability of the $i$-th data association event conditioned by the given measurement:
\begin{align*}
\beta_{i_k} = P[\Theta_i|z_k].
\end{align*}
For the given assumptions summarized in Section \ref{ProbDef}, it can be obtained as
\begin{align}
\beta_{i_k}=\frac{f_{i_k}}{\sum\limits_{y=1}^2 f_{i_k}},\label{eqn:betaik}
\end{align}
where $f_{i_k}$ is defined as
\begin{align}
f_{i_k}=\mathcal{N}[z_{k};\hat z_{i_{k|k-1}},S_{i_k}].
\end{align}
Here $\mathcal{N}[x;\mu,\Sigma]$ denotes the Gaussian probability density function of mean $\mu$ and covariance matrix $\Sigma$ evaluated at $x$ (see Appendix for the derivation of \refeqn{betaik}).

@@

The joint probabilistic data association filter described in the previous section is effective in handling clutter or missed detection of multiple targets. However, it is prone to coalescing estimates, especially with targets in close-proximity. Here, we present a coalescence-avoiding optimal JPDAF, hereafter C-JPDAF for short, to avoid data coalescence. The main idea is choosing the estimator gain such that a weighted sum of the size of uncertainty and a measure of similarity is minimized.

@@

For two probability density functions, $p_1(x)$ and $p_2(x)$, Matusita's measure is defined as
\begin{align*}
\zeta = \int \sqrt{f_1(x)f_2(x) dx},
\end{align*}
which is between 0 and 1, and it measures the similarity between two densities~\cite{Coal_k}.

@@

\begin{figure}
\setlength{\unitlength}{0.1\columnwidth}
\centerline{\footnotesize\selectfont
\begin{picture}(8.5,7.3)(-0.5,-0.8)
\put(-0.5,3){\rotatebox{90}{Cost}}
\put(0,0){\includegraphics[width=0.8\columnwidth]{ECC14_fig1.pdf}}
\put(6.2,0.2){\shortstack[c]{Uncertainty\\ cost: $J_P$}}
\put(6.2,2.8){\shortstack[c]{Similarity\\ cost: $J_S$}}
\put(5.7,5.2){\shortstack[c]{Weighted sum:\\ $J=J_P+cJ_S$}}
\put(4.98,0.78){\circle*{0.1}}
\put(2.48,1.57){\circle*{0.1}}
\put(5.0,-0.3){$K_{JPDA}$}
\put(2.5,-0.3){$K$}
\put(3.1,-0.8){Estimator gain}
\end{picture}
}
\caption{Illustration of optimal coalescence avoidance: several costs are illustrated with respect to the estimator gain $K$ (red: uncertainty cost $J_P$, blue: similarity cost $J_S$, black: weighted sum). The estimator gain $K_{JPDA}$ of JPDA is selected to minimize the uncertainty cost. In the proposed approach, the estimator gain $K$ is chosen such that the weighted sum of the uncertainty cost and the similarity cost is minimized. In short, at the expense of increased uncertainty at a single step, the proposed approach prevents target coalescence. The increased uncertainty at each step is rewarded by reducing the overall estimation error drastically by maintaining correct data association throughout crossing tracks in close proximity.}
%The cost functions of target 1 are examined under the variation of a single element of $K_1$. The resulting cost function (black) is minimized slightly to the right of the uncertainty cost function (blue). Note that the total cost when the Kalman gain is applied does not lie on the total cost curve because other elements of this gain that are not optimal. In Kalman filtering applications, including the JPDAF, only the uncertainty cost function is minimized.}
\label{CostTrends}
\end{figure}

@@

Next, we derive the derivative of each cost. For simplicity, derivatives with respect to the first gain $K_1$ are presented, and derivatives with respect to $K_2$ can be obtain by symmetry. By substituting (\ref{KalCov}) into \refeqn{JP} and using the property $\frac{\partial}{\partial X}\tr{XYX^T}=2XY$ for any matrix $X$ and any symmetric matrix $Y$, we obtain
\begin{align}
\label{CostP}
\frac{\partial J_{P,1}}{\partial K_{1}}&=2\beta_1({K_1S_1-P_1^-H_1^T}).
\end{align}
%
%To appropriately define the similarity cost, we only consider the $R$ term from Equation \ref{R} because coalescence is well known to occur when estimates are within close proximity. For simplicity, we define ${P^+_{12}}^{-1}$ as
%\begin{align}
%{P^+_{12}}^{-1}=(P_1^++P_2^+)^{-1}
%\end{align}
%and define define $u$ as
Substituting (\ref{KalEst}) and (\ref{KalCov}) into \refeqn{u}, and rearranging, 
\begin{align}
u%=&(\hat x^+_1-\hat x^+_2)^T{P^+_{12}}^{-1}(\hat x^+_1-\hat x^+_2)\\
=&\{\hat x_1^{-T}{P^+_{12}}^{-1}\hat x_1^-
-2\hat x_1^{-T}{P^+_{12}}^{-1}\hat x_2^-\nonumber\\
&+2\beta_1(\hat x_1^{-}-\hat x_2^{-})^T{P^+_{12}}^{-1}K_1e_1
+\hat x_2^{-T}{P^+_{12}}^{-1}\hat x_2^-\nonumber\\
&+2\beta_2(\hat x_2^{-}-\hat x_1^{-})^T{P^+_{12}}^{-1}K_2e_2
+\beta_1^2e_1^TK_1^T{P^+_{12}}^{-1}K_1e_1\nonumber\\
&-2\beta_1\beta_2e_2^TK_2^T{P^+_{12}}^{-1}K_1e_1+\beta_2^2e_2^TK_2^T{P^+_{12}}^{-1}K_2e_2\},
\end{align}
where ${P^+_{12}}^{-1}=(P_1^++P_2^+)^{-1}$.

@@

Let $\Iij\in \Re^{n\times m}$ be a $n\times m$ matrix defined such that its $i,j$-th element is one and other elements are zero. The derivative of $(P_{12}^+)^{-1}$ with respect to the $i,j$-th element of $K_1$ is defined as $\mathcal{P}_{ij}\in\Re$:
%such that $ij1(i,j)=1$ and $0$ elsewhere, we define $P^*_{12}$ as
\begin{align}
\mathcal{P}_{ij}&=\frac{\partial {P^+_{12}}^{-1}}{\partial K_{1,ij}}\nonumber\\
&=\beta_1{P_1^+}^{-1}[\Iij H_1P_1^-+P_1^-H_1^T\Iij^T\nonumber\\
&\quad -\Iij S_1K_1^T -K_1S_1\Iij^T]{P_1^+}^{-1}.
\end{align}
Using this, the derivative of $u$ with respect to the $i,j$-th element of $K_1$ can be written as
\begin{align}
\frac{\partial u}{\partial K_{1,ij}}%=&\frac{\partial}{\partial K_{1,ij}}\left\{\hat x^+_1-\hat x^+_2)^T{P^+_{12}}^{-1}(\hat x^+_1-\hat x^+_2\right\}\\
=& \{\hat x_1^{-T}\mathcal{P}_{ij}\hat x_1^-
-2\hat x_1^{-T}\mathcal{P}_{ij}\hat x_2^-\nonumber\\
&+2\beta_1(\hat x_1^{-}-\hat x_2^{-})^T[\mathcal{P}_{ij}K_1+\mathcal{P}_{ij}^{-1}\Iij]e_1\nonumber\\
&+\hat x_2^{-T}\mathcal{P}_{ij}\hat x_2^-+2\beta_2(\hat x_2^{-}-\hat x_1^{-})^T\mathcal{P}_{ij}K_2e_2\nonumber\\
&+\beta_1^2e_1^T[\Iij^T{\mathcal{P}_{ij}}^{-1}K_1+K_1^T\mathcal{P}_{ij}K_1\nonumber\\
&+K_1^T{\mathcal{P}_{ij}}^{-1}\Iij]e_1-2\beta_1\beta_2e_2^TK_2^T[\mathcal{P}_{ij}K_1\nonumber\\
&+{\mathcal{P}_{ij}}^{-1}\Iij]e_1+\beta_2^2e_2^TK_2^T\mathcal{P}_{ij}K_2e_2\}.
\end{align}
From this, the derivation of the similarity cost $J_S$ with respect to the $i,j$-th element of $K_1$ is given by
\begin{align}
\frac{\partial J_{S}}{\partial K_{1,ij}}=-a\exp(-au)\frac{\partial u}{\partial K_{1,ij}}.\label{eqn:JSK}
\end{align}

@@

Three filtering approaches are applied, namely extended Kalman filter (EKF), JPDAF, and C-JPDAF, such that a single measurement was evaluated at each time step, and its origination was random and equally likely from both targets. For EKF, it is assumed that the correct measurement origination is know with certainty, i.e., all of the measurements are associated to correct target. This serves as an ideal reference case to be compared with JPDAF and C-JPDAF. For the C-JPDAF, the weighting parameters of the cost are chosen as $a=0.02$ and $c=5\times10^{-5}$. We propagate the nonlinear equations of motion numerically using Matlab, and we generate measurement at every $0.1$ seconds with an equal likelihood that its origination is from either target.

\begin{figure}
\centerline{
	\subfigure[EKF]{\hspace*{0.07\textwidth}\includegraphics[width=9cm]{EKF.png}\hspace*{0.07\textwidth}}
	}
\centerline{
	\subfigure[JPDAF]{\hspace*{0.07\textwidth}\includegraphics[width=9cm]{JPDAF.png}\hspace*{0.07\textwidth}}
	}
\centerline{
	\subfigure[C-JPDAF]{\hspace*{0.07\textwidth}\includegraphics[width=9cm]{CAOJPDAF.png}\hspace*{0.05\textwidth}}
	}
\caption{Target 1 is represented in blue and target 2 is represented in red. A solid line represents an estimate and a dotted line represents the truth.The JPDAF is subject to coalescence of the neighboring track, causing the estimations to switch trajectories. The C-JPDAF is subject to much less coalescence and hence does not exhibit this problem.}
\label{AllAlgorithms}
\end{figure}

@@

\section{Conclusions and Future Work}
\label{ConclusionFutureWork}
We explore a new approach to reduce coalescence of multiple target tracking. The estimator gains are chosen such that a weighted cost with respect to posterior uncertainty and similarity is minimized. The proximity similarity portion of the Matusita's measure is chosen to evaluate the similarity. Necessary conditions for optimality are derived, and they are solved numerically to obtain optimal estimator gains. Numerical examples illustrate that it exhibits excellent estimation and data association properties for crossing tracks in close proximity. Compared with other techniques to avoid coalescence, the proposed approach has simpler structures. Future works include generalizing C-JPDAF for arbitrary number of targets with clutters, and improving the computational efficiencies.

@@

%%_______________________________________________%
%\section{Data Association Problem Formulation}
%\label{ProbDef}
%% Equations of motion
%\subsection{Equations of Motion}
%Consider a set of linear stochastic discrete-time systems. The equations of motion for the $i$-th system are described by
%\begin{align}
%x_{i_{k+1}} & = A_{i_k} x_{i_k} + w_{i_k},\\
%z_{i_k} & = H_{i_k} x_{i_k} + v_{i_k},
%\end{align}
%where $x_{i_k}\in\Re^n$ is the state vector, $z_{i_k}\in\Re^m$ is the output vector, and  the matrices $A_{i_k}\in\Re^{n\times n}$ and $H_{i_k}\in\Re^{m\times n}$ describe system dynamics and outputs. The process noise and the measurement noise are denoted by $w_{i_k}\in\Re^n$ and $v_{i_k}\in\Re^m$, respectively, and it is assumed that they are zero-mean, mutually independent white, Gaussian noise sequences with known covariance matrices $Q_{i_k}\in\Re^{n\times n}$ and $R_{i_k}\in\Re^{m\times m}$, respectively:
%\begin{align}
%w_{i_k} \sim \mathcal{N}(0,Q_{i_k}),\quad
%v_{i_k} \sim \mathcal{N}(0,R_{i_k}).
%\end{align}
%The initial states are also assumed to be mutually independent and independent to noise. They are Gaussian with known mean values and covariance matrices:
%\begin{align}
%x_{i_k} \sim \mathcal{N}(\bar x_{i_k}, P_{i_k}),
%\end{align}
%where $\bar x_{i_k}\in\Re^n$ and $P_{i_k}\in\Re^{n\times n}$. 
%To demonstrate the main idea of the proposed data association filter concisely, it is assumed that there are two dynamic systems, i.e., $i\in\{1,2\}$. But, the results of this paper are readily generalized to arbitrary number of systems provided the number of systems is known.
%%%%%
%\subsection{Data Association Problem}
%\label{DAP}
%Consider the data association problem when two estimates are in very close proximity.
%For this scenario, several assumptions are made.
%First, we assume that we are only observing a single measurement from this close proximity region, i.e., we consider a single measurement at a time, not a scan of multiple measurements.
%Secondly, we assume that this measurement originates from either one of the targets and not from other sources of clutter; the case when neither target is measured is not considered.
%Like the JPDA, all targets are assumed to fall inside the validation gate.
%Furthermore, the measurement origination between targets is random, unknown, and equally likely. In summary, for the event $\Theta_1$ as measuring target $1$ and the event $\Theta_2$ as measuring target $2$,
%\begin{align}
%P(\Theta_1\cup \Theta_2)&=1,\quad
%P(\Theta_1\cap \Theta_2)=0,\\
%P(\Theta_1)&=P(\Theta_2)=0.5.
%\end{align}
%The only source of knowledge to associate data at time $k$ is the measurement $z_k$.
%Using the estimate prediction $\hat x^-$, we define its prediction
%\begin{align}

>>>>

\documentclass[letterpaper, 10pt, conference]{ieeeconf}
\IEEEoverridecommandlockouts \overrideIEEEmargins
\usepackage{amsmath,amssymb,url}
\usepackage{graphicx,subfigure,tikz,graphicx}
\usepackage{color}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}

@@

\title{\LARGE \bf
%Recursive Kalman-Mahanobis JPDAF Minimization to avoid Coalescence of Estimates in Close Proximity
Optimal Joint Probabilistic Data Association Filter\\ Avoiding Coalescence in Close Proximity }
\author{Evan Kaufman and Taeyoung Lee$^*$
 \thanks{Evan Kaufman and Taeyoung Lee are with Department of Aerospace Engineering, George Washington University, Washington, DC. Email: {\tt\footnotesize \{evankaufman, tylee\}@gwu.edu }}
\thanks{$^*$This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}}

\newcommand{\EditTL}[1]{{\color{red}\protect #1}}
%\renewcommand{\EditTL}[1]{{\protect #1}}

@@

\begin{abstract}
This paper deals with an estimation problem where a known number of targets in close proximity are observed but the measurement originations are uncertain. It is well known that joint probabilistic data association filters (JPDAF) are effective in handing uncertain measurement originations with clutter, but they are prone to estimation coalescence, particularly when close neighboring targets share measurements. This paper proposes a Coalescence Avoiding Optimal JPDAF (C-JPDAF) that minimizes the weighted sum of the posterior uncertainty and a measure of similarity between estimated probability densities. The proposed approach has simpler structures than other coalescence avoiding approaches based on pruning, while exhibiting excellent filtering performance for targets in close proximity with crossing tracks. These are illustrated by a numerical example of two satellites on crossing orbits around the Earth.
%The algorithm is derived and explained, involving a higher computational cost that the JPDAF, but not high enough to prevent the possibility real-time implementation. A numerical example demonstrates how the C-JPDAF is able to maintain the correct trajectories of slowly crossing estimates whereas the JPDAF is not. The results show that the Kalman gain is an effective initial guess for the C-JPDAF, and we discuss the circumstances that warrant the algorithm's use.
\end{abstract}

@@

A variety of data association techniques are considered for close-proximity trajectories with varying performance.
Some approaches such as multiple hypothesis tracking (MHT) and probability hypothesis density (PHD) techniques involve a high computational load, especially when targets are in close proximity, making real-time implementation more difficult~\cite{MHT1},~\cite{PHD1}, and~\cite{PHD2}.
Many other techniques may involve the Kalman filter (KF) or extended KF (EKF), which are well studied and provide a framework for recursive data association techniques that are much easier to implement in real-time.
A common heuristic approach is known as the nearest neighbor filter (NNF), which is a simple algorithm that only updates estimates for measurements with the closest square Mahalnobis distance, updating other targets only with their predictions~\cite{NN2}.
This is considered a \emph{hard decision} in~\cite{JPDAF1}, or that every measurement update receives full weighting; if the decision is incorrect, these measurement updates can result in detrimental effects to the associations of the estimates, so this technique is avoided in the analysis of this paper.
Alternatively, some approaches calculate the minimum mean square error (MMSE) of the estimates and their associated uncertainty.
The probabilistic data association (PDA) technique is effective in tracking a single target because it updates with a \emph{soft decision}; in particular, this approach updates provides a weighting from a likelihood of measurement association.

@@

% Old introduction:

%\section{Introduction}
%Data association has been widely studied with various applications in estimation of a single or multiple targets with measurements that are not necessarily originating from correct targets in order. To properly track multiple targets with measurement origin uncertainties, measured data should be properly associated to targets with certain probabilities. %When the targets are in very close proximity, the association uncertainty grows, and an effective algorithm is required to maintain close estimations of the targets. Otherwise, estimators tend to coalesce neighboring tracks. 
%%This paper considers estimation wherein multiple targets of interest enter the field of view of a sensor; however, the measurement origin is unknown. 
%A variety of data association techniques with varying performance have been studied. A common heuristic approach is known as the nearest neighbor filter (NNF), where measurements with the closest distance are only applied~\cite{NN2}. This is considered a \emph{hard decision} in~\cite{JPDAF1}, as every selected measurement update receives full weighting. Therefore, if the decision is incorrect, these measurement updates can result in detrimental effects to the associations of the estimates.  Alternatively, there are approaches that calculate the minimum mean square error (MMSE) of the estimates and their associated uncertainty. The probabilistic data association (PDA) technique is effective in tracking a single target because it updates with a \emph{soft decision}; in particular, this approach updates provides a weighting from a likelihood of measurement association. Other approaches include multiple hypothesis tracking (MHT) and probability hypothesis density (PHD) techniques~\cite{MHT1,PHD1,PHD2}. 
%%Many other techniques may involve the Kalman filter (KF) or extended KF (EKF), which are well studied and provide a framework for recursive data association techniques that are much easier to implement in real-time.
%The joint PDA (JPDA) is an extension of the PDA to incorporate multiple targets~\cite{JPDAF1},~\cite{TrackDataAssoc}.
%The JPDA filter (JPDAF) is particularly advantageous in multi-target scenarios because when targets share measurements, the soft decisions prevent loss of information that occurs with hard decisions. As such, it is well known that JPDAF are effective in handling data clutter or missed detection. However, when the targets are in very close proximity, the association uncertainty grows significantly, thereby degrading the filtering performance. Furthermore, the estimated probability distributions tend to be coalesced especially if the paths of neighboring targets cross with each other. 
%%neighboring targets share measurements, the estimates are subject to coalescence.
%Many techniques to avoid track coalescence involve the concept that when the exact nearest neighbor probabilistic data association (ENNPDA) is applied, which associates a measurement with a strong decision to the most likely estimate, the estimates are insensitive to track coalescence~\cite{Coal1}. By pruning the tracks, or designing a set of rules to determine high likelihood scenarios, an algorithm choice or weighing scheme is applied to the measurement updates.
%For example in~\cite{Fitzgerald}, the algorithm involves a set of rules based on the data received with respect to the estimates. A special logic is introduced that determines how weighting of the updates is defined or if a new track should be considered. In some cases, it is possible for an incorrectly associated estimate measurement may receive full weighting in the update. Other criteria or extensions of this approach are detailed in~\cite{Coal_d},~\cite{Coal_e}, and~\cite{Coal_c}, which can be very effective, but information may be lost when measurements are omitted from updating an estimates with small probabilities of association because the pruning rule prevented these association possibilities.
%This paper is focused on optimal joint probabilistic data association filter that avoids coalescence in close proximity. We propose a novel approach to remove coalescence by minimizing a similarity index of the estimates. More explicitly, the gain of the proposed estimator is chosen such that a weighted sum of the size of uncertainties and a similarity measure between estimated states is minimized at each update. This yields an optimal recursive estimation algorithm that compensates for the effects of coalescence systematically. The proposed approach has simpler structures compared with pruning-based approaches, and it is computationally efficient. As it is still based on probabilistic data association, it avoids the heuristic nature, loss of information, or the risk of other coalescence avoidance approaches based on hard-decision.
%The paper is organized as follows: the dynamics of target and the measurement models are described in Section \ref{ProbDef}. The proposed Coalescence Avoiding Optimal JPDAF (C-JPDAF) are presented at Sections \ref{JPDAF}, and the optimal gain that minimizes a weighted cost of uncertainty and similarity is derived in Section \ref{C-JPDAF}.
%These are illustrated by a numerical example for estimating two satellites in crossing orbits in Section \ref{NumRes}, followed by conclusions in Section \ref{ConclusionFutureWork}.

\section{Data Association Filtering Problem Formulation}
\label{ProbDef}

@@

More explicitly, let $\Theta_i$ be the event that the measurement originates from the $i$-th target, for $i\in\{1,2\}$. According to the above assumptions, we have
\begin{align}
P(\Theta_1\cup \Theta_2)&=1,\quad
P(\Theta_1\cap \Theta_2)=0,\\
P(\Theta_1)&=P(\Theta_2)=0.5.\label{eqn:MeaOrig}
\end{align}

@@

Joint probabilistic data association filter is a suboptimal Bayesian filter for multiple targets where the probabilities of association are computed for the latest set of measurements only~\cite{TrackDataAssoc}. This section summarizes the approaches of JPDAF.

@@

The date association probability is defined as follows. Let $\beta_i$ be the probability of the $i$-th data association event conditioned by the given measurement:
\begin{align*}
\beta_{i_k} = P[\Theta_i|z_k].
\end{align*}
For the given assumptions summarized in Section \ref{ProbDef}, it can be obtained as
\begin{align}
\beta_{i_k}=\frac{f_{i_k}}{\sum\limits_{y=1}^2 f_{i_k}},\label{eqn:betaik}
\end{align}
where $f_{i_k}$ is defined as
\begin{align}
f_{i_k}=\mathcal{N}[z_{k};\hat z_{i_{k|k-1}},S_{i_k}].
\end{align}
Here $\mathcal{N}[x;\mu,\Sigma]$ denotes the Gaussian probability density function of mean $\mu$ and covariance matrix $\Sigma$ evaluated at $x$ (see Appendix for the derivation of \refeqn{betaik}).

@@

The joint probabilistic data association filter described in the previous section is effective in handling clutter or missed detection of multiple targets. However, it is prone to coalescing estimates, especially with targets in close-proximity. Here, we present a coalescence-avoiding optimal JPDAF, hereafter C-JPDAF for short, to avoid coalescence of the estimates. The main idea is choosing the estimator gain such that a weighted sum of the size of uncertainty and a measure of similarity is minimized.

@@

For two probability density functions, $f_1(x)$ and $f_2(x)$, Matusita's measure is defined as
\begin{align*}
\zeta = \int \sqrt{f_1(x)f_2(x) dx},
\end{align*}
which is between 0 and 1, and it measures the similarity between two densities~\cite{Coal_k}.

@@

\begin{figure}
\setlength{\unitlength}{0.1\columnwidth}
\centerline{\footnotesize\selectfont
\begin{picture}(8.5,7.3)(-0.5,-0.8)
\put(-0.5,3){\rotatebox{90}{Cost}}
\put(0,0){\includegraphics[width=0.8\columnwidth]{ECC14_fig1.pdf}}
\put(6.2,0.2){\shortstack[c]{Uncertainty\\ cost: $J_P$}}
\put(6.2,2.8){\shortstack[c]{Similarity\\ cost: $J_S$}}
\put(5.7,5.2){\shortstack[c]{Weighted sum:\\ $J=J_P+cJ_S$}}
\put(4.98,0.78){\circle*{0.1}}
\put(2.48,1.57){\circle*{0.1}}
\put(5.0,-0.3){$K_{JPDA}$}
\put(2.5,-0.3){$K$}
\put(3.1,-0.8){Estimator gain}
\end{picture}
}
\caption{Illustration of optimal coalescence avoidance: several costs are illustrated with respect to the estimator gain $K$ (red: uncertainty cost $J_P$, blue: similarity cost $J_S$, black: weighted sum). The estimator gain $K_{JPDA}$ of JPDA is selected to minimize the uncertainty cost. In the proposed approach, the estimator gain $K$ is chosen such that the weighted sum of the uncertainty cost and the similarity cost is minimized. In short, at the expense of increased uncertainty at a single step, the proposed approach prevents coalescence. The increased uncertainty at each step is rewarded by reducing the overall estimation error drastically by maintaining correct data association throughout crossing tracks in close proximity.}
%The cost functions of target 1 are examined under the variation of a single element of $K_1$. The resulting cost function (black) is minimized slightly to the right of the uncertainty cost function (blue). Note that the total cost when the Kalman gain is applied does not lie on the total cost curve because other elements of this gain that are not optimal. In Kalman filtering applications, including the JPDAF, only the uncertainty cost function is minimized.}
\label{CostTrends}
\end{figure}

@@

Next, we derive the derivative of each cost. For simplicity, derivatives with respect to the first gain $K_1$ are presented, and derivatives with respect to $K_2$ can be obtained by symmetry. By substituting (\ref{KalCov}) into \refeqn{JP} and using the property $\frac{\partial}{\partial X}\tr{XYX^T}=2XY$ for any matrix $X$ and any symmetric matrix $Y$, we obtain
\begin{align}
\label{CostP}
\frac{\partial J_{P,1}}{\partial K_{1}}&=2\beta_1({K_1S_1-P_1^-H_1^T}).
\end{align}
%
%To appropriately define the similarity cost, we only consider the $R$ term from Equation \ref{R} because coalescence is well known to occur when estimates are within close proximity. For simplicity, we define ${P^+_{12}}^{-1}$ as
%\begin{align}
%{P^+_{12}}^{-1}=(P_1^++P_2^+)^{-1}
%\end{align}
%and define define $u$ as
Substituting (\ref{KalEst}) and (\ref{KalCov}) into \refeqn{u}, and rearranging, 
\begin{align}
u%=&(\hat x^+_1-\hat x^+_2)^T{P^+_{12}}^{-1}(\hat x^+_1-\hat x^+_2)\\
=&\{\hat x_1^{-T}{P^+_{12}}^{-1}\hat x_1^-
-2\hat x_1^{-T}{P^+_{12}}^{-1}\hat x_2^-\nonumber\\
&+2\beta_1(\hat x_1^{-}-\hat x_2^{-})^T{P^+_{12}}^{-1}K_1e_1
+\hat x_2^{-T}{P^+_{12}}^{-1}\hat x_2^-\nonumber\\
&+2\beta_2(\hat x_2^{-}-\hat x_1^{-})^T{P^+_{12}}^{-1}K_2e_2
+\beta_1^2e_1^TK_1^T{P^+_{12}}^{-1}K_1e_1\nonumber\\
&-2\beta_1\beta_2e_2^TK_2^T{P^+_{12}}^{-1}K_1e_1+\beta_2^2e_2^TK_2^T{P^+_{12}}^{-1}K_2e_2\},
\end{align}
where ${P^+_{12}}^{-1}=(P_1^++P_2^+)^{-1}$.

@@

Let $\Iij\in \Re^{n\times m}$ be a $n\times m$ matrix defined such that its $i,j$-th element is one and other elements are zero. The derivative of $(P_{12}^+)^{-1}$ with respect to the $i,j$-th element of $K_1$ is defined as $\mathcal{P}_{ij}\in\Re$:
%such that $ij1(i,j)=1$ and $0$ elsewhere, we define $P^*_{12}$ as
\begin{align}
\mathcal{P}_{ij}&=\frac{\partial {P^+_{12}}^{-1}}{\partial K_{1,ij}}\nonumber\\
&=\beta_1{P_1^+}^{-1}[\Iij H_1P_1^-+P_1^-H_1^T\Iij^T\nonumber\\
&\quad -\Iij S_1K_1^T -K_1S_1\Iij^T]{P_1^+}^{-1}.
\end{align}
Using this, the derivative of $u$ with respect to the $i,j$-th element of $K_1$ can be written as
\begin{align}
\frac{\partial u}{\partial K_{1,ij}}%=&\frac{\partial}{\partial K_{1,ij}}\left\{\hat x^+_1-\hat x^+_2)^T{P^+_{12}}^{-1}(\hat x^+_1-\hat x^+_2\right\}\\
=& \{\hat x_1^{-T}\mathcal{P}_{ij}\hat x_1^-
-2\hat x_1^{-T}\mathcal{P}_{ij}\hat x_2^-\nonumber\\
&+2\beta_1(\hat x_1^{-}-\hat x_2^{-})^T[\mathcal{P}_{ij}K_1+{P^+_{12}}^{-1}\Iij]e_1\nonumber\\
&+\hat x_2^{-T}\mathcal{P}_{ij}\hat x_2^-+2\beta_2(\hat x_2^{-}-\hat x_1^{-})^T\mathcal{P}_{ij}K_2e_2\nonumber\\
&+\beta_1^2e_1^T[\Iij^T{P^+_{12}}^{-1}K_1+K_1^T\mathcal{P}_{ij}K_1\nonumber\\
&+K_1^T{P^+_{12}}^{-1}\Iij]e_1-2\beta_1\beta_2e_2^TK_2^T[\mathcal{P}_{ij}K_1\nonumber\\
&+{P^+_{12}}^{-1}\Iij]e_1+\beta_2^2e_2^TK_2^T\mathcal{P}_{ij}K_2e_2\}.
\end{align}
From this, the derivation of the similarity cost $J_S$ with respect to the $i,j$-th element of $K_1$ is given by
\begin{align}
\frac{\partial J_{S}}{\partial K_{1,ij}}=-a\exp(-au)\frac{\partial u}{\partial K_{1,ij}}.\label{eqn:JSK}
\end{align}

@@

%\EditTL{Put the values of $P_0$, $Q$ and $R$ here. Describe how the measurements are switched between two satellites. }

Three filtering approaches are applied, namely extended Kalman filter (EKF), JPDAF, and C-JPDAF. For the EKF, it is assumed that the correct measurement origination is know with certainty, i.e., all of the measurements are associated to the correct target. This serves as an ideal reference case to be compared with JPDAF and C-JPDAF. For the C-JPDAF, the weighting parameters of the cost are chosen as $a=0.02$ and $c=5\times10^{-5}$. We propagate the nonlinear equations of motion numerically using Matlab, and we generate a measurement at every $0.1$ seconds with an equal likelihood that its origination is from either target such that identical noisy measurements are used in all three algorithms.

\begin{figure}
\centerline{
	\subfigure[EKF]{\hspace*{0.07\textwidth}\includegraphics[width=9cm]{EKF.png}\hspace*{0.07\textwidth}}
	}
\centerline{
	\subfigure[JPDAF]{\hspace*{0.07\textwidth}\includegraphics[width=9cm]{JPDAF.png}\hspace*{0.07\textwidth}}
	}
\centerline{
	\subfigure[C-JPDAF]{\hspace*{0.07\textwidth}\includegraphics[width=9cm]{CAOJPDAF.png}\hspace*{0.05\textwidth}}
	}
\caption{Target 1 is represented in blue and target 2 is represented in red. A solid line represents an estimate and a dotted line represents the truth. The JPDAF is subject to coalescence of the neighboring track, causing the estimations to switch trajectories. The C-JPDAF is subject to much less coalescence and hence does not exhibit this problem.}
\label{AllAlgorithms}
\end{figure}

@@

\section{Conclusions and Future Work}
\label{ConclusionFutureWork}
We explore a new approach to reduce coalescence of close proximity multi-target tracking. The estimator gains are chosen such that a weighted cost with respect to posterior uncertainty and similarity is minimized. The proximity similarity portion of the Matusita's measure is chosen to evaluate the similarity. Necessary conditions for optimality are derived, and they are solved numerically to obtain optimal estimator gains. Numerical examples illustrate that it exhibits excellent estimation and data association properties for crossing tracks in close proximity. Compared with other techniques to avoid coalescence, the proposed approach has simpler structures. Future works include generalizing C-JPDAF for arbitrary number of targets with clutter, and improving the computational efficiencies.

@@
